\input{pream}
\title{Advanced Data Management - Assignment 3}
\author{S\o ren Bjerregaard Vrist\\ITU Copenhagen}

\begin{document}
\maketitle

\chapter{Log book over experiments}

\section{Part 1}

\begin{itemize}
\item[2010-04-08:] Spent all day trying to install spatial extensions for db2.
To no avail. The installer cant see which BASE_DB2_ENGINE is installed. The
\verb|db2ls -q -b <something>| is empty
\end{itemize}

\section{Part2}

\appendix
\chapter{Appendix}
\section{Profwrites2.py}\label{app:prof}
New edition of the writes.py that does work on subsequent runs as well as no
shared mutex.
\lstinputlisting{assignment2/profwrites2.py}

\section{writestl.py}\label{app:tl}
New edition of the writes.py that contains a tablelocking switch.
\lstinputlisting{assignment2/writestl.py}

\section{setup.bash and experiment execution}\label{app:setup}
To even out any ec2 glitches I ran the experiements several times:
\begin{verbatim}
$ for i in `seq 3`; 
do 
   echo $i; 
   bash run1.bash; 
   bash run2.bash; 
   bash tl.bash; 
done
\end{verbatim}

\subsection{Tool script included by all experiment specific scripts}
\lstinputlisting{assignment2/setup.bash}

\subsection{Experiment scripts for assignment2-part1}

Part1a:\\
Different threadcounts and index/private key/append mode for tables.
\lstinputlisting{assignment2/run1.bash}
Part1a:\\
Experiment with LOGBUFSZ, CHNGPGS\_THRES values.
\lstinputlisting{assignment2/run2.bash}
Part1b:\\
Tablelocking both insert and updates.
\lstinputlisting{assignment2/tl.bash}

\end{document}
